A High Efficiency MAC Protocol for WLANs: Providing Fairness in Dense Scenarios

### 2015-11-03 results.tex
Fixed figures, checked L-ZC. Final read pending

@@

	\begin{figure}[tb]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/blockingProb-unsat/blocking-unsaturated-TON.eps}
		\caption{Average fraction of blocked packets. When the MAC queue is full, packets comming from the uppers are discarded (or blocked) at the entrance of the buffer}
		\label{fig:blocked-packets}
	\end{figure}

@@

	\begin{figure*}[tb]
		\centering
		\includegraphics[width=0.5\linewidth,angle=-90]{figures/tonFigs/coexistence-combined.eps}
		\caption{Coexistence results: a) Network throughput when composed by various proportions of CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes; b) Average percentage of collision slots for the tested mixed network setups proportions; c) Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes; d) Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions; e) Average station throughput per MAC protocol in a saturated mixed network}
		\label{fig:coexResults}
	\end{figure*}

@@

	\textcolor{red}{Still referring to Figure~\ref{fig:coexResults}e, for $N^{*}>12$ periods of collision-free operation and the aggregation performed with Fair Share allows CSMA/ECA$_{\text{Hys+FS}}$ to have larger channel time than CSMA/CA nodes, which throughput degrades even more than in CSMA/CA-only. These results suggests that a switch to CSMA/ECA$_{\text{Hys+FS}}$ can be beneficial for networks with high number of contenders are expected.}

>>>>

	\begin{figure}[htb!]
		\centering
		\includegraphics[width=0.7\linewidth,angle=-90]{figures/unsaturated/blockingProb-unsat/blocking-unsaturated-TON.eps}
		\caption{Average fraction of blocked packets. When the MAC queue is full, packets comming from the uppers are discarded (or blocked) at the entrance of the buffer}
		\label{fig:blocked-packets}
	\end{figure}

@@

@@

	\begin{figure*}[tb]
		\centering
		\includegraphics[width=0.5\linewidth,angle=-90]{figures/tonFigs/coexistence-combined.eps}
	\caption{Coexistence results: a) Network throughput when composed by various proportions of saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes; b) Average percentage of collision slots for the tested saturated mixed network setups proportions; c) Network throughput when composed by various proportions of non-saturated CSMA/CA and CSMA/ECA$_{\text{Hys+FS}}$ nodes; d) Average percentage of collision slots for the tested mixed network setups proportions in non-saturated conditions; e) Average station throughput per MAC protocol in a saturated mixed network}
		\label{fig:coexResults}
	\end{figure*}

@@

	\textcolor{red}{Still referring to Figure~\ref{fig:coexResults}e, for $N^{*}>12$ periods of collision-free operation and the aggregation performed with Fair Share allows CSMA/ECA$_{\text{Hys+FS}}$ to have larger channel time than CSMA/CA nodes, which throughput degrades even more than in CSMA/CA-only. These results suggests that a switch to CSMA/ECA$_{\text{Hys+FS}}$ can be beneficial for networks with high number of contenders.}

### 2015-11-03 transition.tex
Fixed figures, checked L-ZC. Final read pending

\begin{itemize}
	\item The performance of a CSMA/ECA$_{\text{Hys+FS}}$ network in presence of hidden nodes: transmissions from stations in the same or other networks may negatively affect the collision-free operation, particularly when not all devices in the CSMA/ECA$_{\text{Hys+FS}}$ WLAN are able to listen such transmissions. As a consequence, not all stations will pause the backoff countdown accordingly, resulting in large slot drifts that disrupt any collision-free schedule, approximating CSMA/ECA$_{\text{Hys+FS}}$ performance to CSMA/CA's.

>>>>

\begin{itemize}
	\item The performance of CSMA/ECA$_{\text{Hys+FS}}$ WLANs in dense scenarios: transmissions from stations in the same or other networks may negatively affect the collision-free operation, particularly when not all devices in the CSMA/ECA$_{\text{Hys+FS}}$ WLAN are able to listen such transmissions. As a consequence, not all stations will pause the backoff countdown accordingly, resulting in large slot drifts that disrupt any collision-free schedule, approximating CSMA/ECA$_{\text{Hys+FS}}$ performance to CSMA/CA's.
